### 2013-07-11 miscellaneous/inverse-limit-seminar-summer-2013/results.tex
Updated inverse limits

\input{../header.tex}

@@

For (3), we need only observe that for any sequence $\alpha\in K$, an open neighborhood of $\alpha$ would contain infinte sequences $\beta$ such that $\alpha(N)=\beta(N)$.

>>>>

\input{../../header.tex}

@@

For (3), it is easy to show that for any sequence $\alpha\in L \cap \prod_{n=1}^\infty [a_n,b_n]$ where $0\leq a_N < b_N < 1$ for some $N$, an open neighborhood of $\alpha$ would contain infinte sequences $\beta$ with $\alpha(N)=\beta(N)$ and $\beta(p)>b_p$ for some number $p$.
